thesis2024

### 2025-05-02 article1.qmd
Macbook session. Tests to latex chapter structure 01
More experimentation on aesthetics

---
execute:
  echo: false
  warning: false
  message: false
  comment: "#>"
  fig-path: "../figures/creating-frames/"
  fig-dpi: 600
---

@@

# Creating frames of reference for chert exploitation during the Late Pleistocene in Southwesternmost Iberia

**Authors**: Joana Belmiro, Xavier Terradas, João Cascalheira

@@

>>>>

---
execute:
  echo: false
  warning: false
  message: false
  comment: "#>"
  fig-path: "../figures/creating-frames/"
  fig-dpi: 600

---

@@

# Creating frames of reference for chert exploitation during the Late Pleistocene in Southwesternmost Iberia
Joana Belmiro^1^, Xavier Terradas^2^, João Cascalheira^1^

^1^ Interdisciplinary Center for Archaeology and the Evolution of Human Behaviour, University of Algarve, Portugal; ^2^ Spanish National Research Council - Institute Milá y Fontanals of research on Humanities, Barcelona, Spain

**Publication reference**: Belmiro, Joana, Xavier Terradas, and João Cascalheira. 2023. “Creating Frames of Reference for Chert Exploitation during the Late Pleistocene in Southwesternmost Iberia.” PLOS ONE 18 (10). https://doi.org/10.1371/journal.pone.0293223.

@@

**Keywords**: Chert raw material; Petrography; Southern Portugal; Provenance studies

### 2025-05-02 thesis2024.tex
More experimentation on aesthetics

\renewcommand*\contentsname{Table of contents}
{
\hypersetup{linkcolor=}
\setcounter{tocdepth}{2}
\tableofcontents
}

\setstretch{1.5}
\bookmarksetup{startatroot}

@@

\chapter*{Abstract}\label{abstract-1}
\addcontentsline{toc}{chapter}{Abstract}

\markboth{Abstract}{Abstract}

\chapter{Creating frames of reference for chert exploitation during the Late Pleistocene in Southwesternmost Iberia}

\textbf{Authors}: Joana Belmiro, Xavier Terradas, João Cascalheira

@@

\section*{Introduction}\label{introduction-1}
\addcontentsline{toc}{section}{Introduction}

\markright{Introduction}

@@

\section*{Geological setting and chert
groups}\label{geological-setting-and-chert-groups}
\addcontentsline{toc}{section}{Geological setting and chert groups}

\markright{Geological setting and chert groups}

\subsection*{Geological setting}\label{geological-setting}
\addcontentsline{toc}{subsection}{Geological setting}

@@

\subsection*{Chert outcrops}\label{chert-outcrops}
\addcontentsline{toc}{subsection}{Chert outcrops}

@@

\section*{Materials and methods}\label{materials-and-methods}
\addcontentsline{toc}{section}{Materials and methods}

\markright{Materials and methods}

@@

\section*{Results}\label{results}
\addcontentsline{toc}{section}{Results}

\markright{Results}

@@

\subsection*{Western Algarve}\label{western-algarve}
\addcontentsline{toc}{subsection}{Western Algarve}

@@

\subsection*{Eastern Algarve}\label{eastern-algarve}
\addcontentsline{toc}{subsection}{Eastern Algarve}

@@

\subsection*{Other outcrops}\label{other-outcrops}
\addcontentsline{toc}{subsection}{Other outcrops}

@@

\section*{Discussion}\label{discussion}
\addcontentsline{toc}{section}{Discussion}

\markright{Discussion}

@@

\section*{Conclusion}\label{conclusion}
\addcontentsline{toc}{section}{Conclusion}

\markright{Conclusion}

@@

>>>>

\renewcommand*\contentsname{Table of contents}
{
\hypersetup{linkcolor=}
\setcounter{tocdepth}{2}
\tableofcontents
}
\listoffigures
\listoftables

\setstretch{2}
\bookmarksetup{startatroot}

@@

\chapter{Creating frames of reference for chert exploitation during the
Late Pleistocene in Southwesternmost
Iberia}\label{creating-frames-of-reference-for-chert-exploitation-during-the-late-pleistocene-in-southwesternmost-iberia}

Joana Belmiro\textsuperscript{1}, Xavier Terradas\textsuperscript{2},
João Cascalheira\textsuperscript{1}

\textsuperscript{1} Interdisciplinary Center for Archaeology and the
Evolution of Human Behaviour, University of Algarve, Portugal;
\textsuperscript{2} Spanish National Research Council - Institute Milá y
Fontanals of research on Humanities, Barcelona, Spain

\textbf{Publication reference}: Belmiro, Joana, Xavier Terradas, and
João Cascalheira. 2023. ``Creating Frames of Reference for Chert
Exploitation during the Late Pleistocene in Southwesternmost Iberia.''
PLOS ONE 18 (10). https://doi.org/10.1371/journal.pone.0293223.

\section*{Abstract}\label{abstract-1}
\addcontentsline{toc}{section}{Abstract}

@@

\textbf{Keywords}: Chert raw material; Petrography; Southern Portugal;
Provenance studies

\section{Introduction}\label{introduction-1}

@@

\section{Geological setting and chert
groups}\label{geological-setting-and-chert-groups}

\subsection{Geological setting}\label{geological-setting}

@@

\subsection{Chert outcrops}\label{chert-outcrops}

@@

\section{Materials and methods}\label{materials-and-methods}

@@

\section{Results}\label{results}

@@

\subsection{Western Algarve}\label{western-algarve}

@@

\subsection{Eastern Algarve}\label{eastern-algarve}

@@

\subsection{Other outcrops}\label{other-outcrops}

@@

\section{Discussion}\label{discussion}

@@

\section{Conclusion}\label{conclusion}

@@

\pagebreak
